%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeIte}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeItemLang}[3]{
  \item\small{
    \textbf{#1} \textit{#2}{: #3 \vspace{-2pt}}
  }\vspace{-4pt}
}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Omar Amin}} & Email :
    \href{mailto:omaramin4@gmail.com}{omaramin4@gmail.com}\\
  \href{https://github.com/omarfos}{https://github.com/omarfos} & Mobile : +1-347-774-4388
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cornell University}{Ithaca, NY}
      {Master of Engineering in Computer Science}{Expected Graduation: May 2021}
    \resumeSubheading
      {Stony Brook University}{Stony Brook, NY}
      {Bachelor of Science in Computer Science, GPA: 3.76 }{Aug. 2015 -- May.  2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{American Express} & New York City, NY
    \end{tabular*}\vspace{-5pt}

    \resumeSubSubheading
     {Digital Workplace Team}{Summer 2020}
     \resumeItemListStart
        \resumeIte
          {Enhanced safety of 10000 employees by building an
          application to enforce
          COVID-19 guidelines.}
     \resumeItemListEnd

    \resumeSubSubheading
     {Intelligent Automation Team}{Summer 2019}
      \resumeItemListStart
        \resumeIte
          {Reduced training time by over 300\% by building an intuitive and easy
          to use React interface for labeling documents from AWS S3 and
          automatically updating the corresponding ML model.}
        \resumeIte
          {Worked with ML team to implement a Document Classification and
          Optical Character Recognition API using Java and Spring Boot
          microservices.}
        \resumeIte
          {Improved customer service representatives' productivity by 10\% by
          automating the KYC process by using Netflix Conductor to orchestrate
          workflows.}
        \resumeIte 
          {Won first place in a hackathon out of 40 teams by creating a service for managing customers' subscriptions and providing
          analytics using React.}
      \resumeItemListEnd

      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Stony Brook University}{Stony Brook, NY}
      {Algorithms Teaching and Research Assistant}{Spring 2019 and Fall 2019}
      \resumeItemListStart
        \resumeIte
          {Increased class median by 5\% by leading a team of 4 undergraduate
          TAs, holding weekly review sessions, and creating effective practice
          exams.}
        \resumeIte
          {Compiled over 100 exercises and diagrams for \textit{The Algorithm
          Design Manual}.
          }
          %\vspace{-5pt}
      \resumeItemListEnd
      \vspace{-5pt}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeItemLang{Hack Together}{Flask, React}
      {Website for people to simultaneously compete in solving
      algorithmic questions, which can be queried by difficulty, topic, and
      company.}
    \resumeItemLang{College For Me}{Django, React}
    {Website for high school students to
    record their college applications and to get intelligent recommendations and
    metrics.}
    \resumeItemLang{Xv6 Projects}{C, Intel x86}{
      Various projects involving MIT's port of the UNIX v6 operating system such as a shell, a new
      thread scheduling algorithm, utilities, virtual memory, and a file system.   
    }
    \resumeItemLang{Asynchronous Job Server}{C, Linux}{High performance Linux
    server utilizing the latest system calls that accepts concurrent jobs from
    clients and provides accounting and resource information.}
    \resumeItemLang{Malloc Library}{C}{A wrapper over malloc that's able to
    detect and report common C bugs involving pointers and memory corruption. In
    addition, I created a specialized memory allocator that utilizes
    segregated quick lists.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages (10000+ lines of code)}
      {Python, C, Java}
    \resumeSubItem{Technologies}
      {Django, React, Spring Boot, AWS}
  \resumeSubHeadingListEnd

%-------------------------------------------

%-----------PROJECTS-----------------
% \section{Courses}
  % \resumeSubHeadingListStart
    % \resumeSubItem{Graduate}
      % {System Security, Wireless and Mobile Networks; \textit{Intented:} Distributed Systems, Machine Learning, Natural
      % Language Processing}
    % \resumeSubItem{Undergraduate}
      % {Operating Systems, Computational Geometry, Data Science, Artificial Intelligence}
  % \resumeSubHeadingListEnd

\section{Additional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Professional Gamer}{Los Angeles, CA}
      {Game: League of Legends; Team: Counter Logic Gaming}{Dec. 2016 - May. 2018}
      \resumeItemListStart
        \resumeItem{Competitions}
          {On a sabbatical from university, I competed internationally in
          \textit{League of Legends} tournaments for the team, \textit{Counter
          Logic Gaming}. I was recruited after placing top 10 out of a million
          players on the solo rankings.}
      \resumeItemListEnd
      \vspace{-5pt}
  \resumeSubHeadingListEnd
\end{document}
